Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing

### 2021-01-14 Dissonance_Santiago_v3/Response-to-Reviewers-v3.Rmd

---
title: "Response to Reviewers"
output: pdf_document
---

We would like to thank the editor and three anonymous reviewers for their thoughtful comments and suggestions for revisions. We believe that the paper has been substantially improved by their input and we hope that they will find this version to fully address all their comments. In this letter we respond to the feedback received, and describe the actions taken to revise the paper.

\newpage

# Reviewer 1

You have helpfully structured your responses to the initial review, so your actions relating to this review can be seen. I am not entirely satisfied with some of your responses. For instance whilst Figures 1 and 2 may have been improved, they still look fairly 'amateur'. Also I am not fully satisfied that the explanation of how affective values were chosen has been substantially and explicitly acted upon. However, on my first review I considered this a good paper needing iterative improvements. I feel such improvements have been made. It is a well written paper, and better than it was, with a strong and clear narrative, an interesting topic, and detailed and extensive findings. I therefore recommend it be published.

>\textcolor{blue}{Thank you very much for your suggestions to improve the paper and for endorsing it for publication.}

\newpage

# Reviewer 2

The manuscript has been improved. It is now easier to follow the arguments and the different choices that the authors make in method, design, and analysis. I have a few minor comments.

>\textcolor{blue}{Thank you again for your suggestions to improve the paper and for endorsing it for publication.}

K-12 is still not explained (Figure 1). I do not know what it stands for.

>\textcolor{blue}{This is now explained in section 3.2, where we note that there are three levels of education, one of which is Kindergarten to grade 12, or K-12.}

Paragraph 3 is fuzzy and can be clarified. Remove redundant information and stick to the specific contribution. Then, compare points 1, 2 and 3 with the objectives presented later in the paper (e.g., line 247). It is important that the purpose is reproduced correctly throughout the paper.

>\textcolor{blue}{As noted in our response to Reviewer 1, we moved comments about literature towards the section of concluding remarks; leaving some results in the introductory section.}

Line 102 and 142. It is not common to write out the full name in references. "Cecilia" used in the reference Cecilia Jakobsson Bergstad et al., 2011 is her first name. "Cecilia" should be removed.

>\textcolor{blue}{True. We have modified that now.}

Line 105 and 147. Replace C. J. Bergstad et al., 2011 with Jakobsson Bergstad et al., 2011

>\textcolor{blue}{Done.}

Line 106/107. Remove " but see…"

>\textcolor{blue}{Done.}

Line 156/157. Replace bold text with normal text

>\textcolor{blue}{Done.}

Line 156. Replace Olson with Olsson

>\textcolor{blue}{Done.}

Line 273. significant at better than" remove "at"

>\textcolor{blue}{Done.}

Line 277. "In the case…" replace with "In this case"

>\textcolor{blue}{Done.}

Line 331. "…differences at better than 10%" remove "at"

>\textcolor{blue}{Done.}

Line 381. Misspelling of "Transportatoin"

>\textcolor{blue}{Done.}

Line 390. "Whereas" replace "W" with a lower-case "w" (don’t find that correct)

>\textcolor{blue}{Done.}

Reading difficulties in figure 3, 4 and 7. Check travel mode.

>\textcolor{blue}{We recreated this figures to remove some cluttering, hopefully increasing their readability.}

Please use upper-cases (e.g. line 391) or lower-cases (e.g., 409) for affective values throughout the manuscript.

>\textcolor{blue}{We have revised the manuscript to use upper case consistently.}

Line 514/515. Please check the sentence: "Luxury and status, on the other hand, are more frequently associated to luxury and status."

>\textcolor{blue}{Corrected.}

\newpage

# Reviewer 3

The authors have addressed my concerns and the paper looks strong. Hence, I recommend it for publication.

>\textcolor{blue}{Thank you again for your useful feedback and for endorsing the paper for publication.}

### 2021-01-14 Dissonance_Santiago_v3/Dissonance_Santiago_Title_Page_v3.Rmd
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

---
title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
author:
  - name: Beatriz Mella Lira
    email: beatriz.lira.14@ucl.ac.uk
    affiliation: PUC
    footnote: Corresponding Author
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
address:
  - code: PUC
    address: BRT+ Centre of Excellence, Departamento Ingeniería de Transporte y Logística, Escuela de Ingeniería, Pontificia Universidad Católica de Chile
  - code: McMaster University
    address: School of Earth, Environment, and Society, McMaster University, 1280 Main St W, Hamilton, Ontario, L8S 1S4 Canada
abstract: |
   *Introduction*  
   Subjective wellbeing is a topic that has attracted considerable attention in the transportation literature in recent years. As a result, there is a burgeoning literature that investigates the impacts of travel on subjective wellbeing, and how wellbeing, in turn, can influence behavior. An important aspect of subjective wellbeing are the affective reactions of people to their experiences.   
   *Objective*  
   The objective of this paper is to analyze the affective reactions of travelers with respect to various modes of transportation. In particular, we are interested in the potential for dissonance between primary mode of travel and the mode(s) of travel identified as evoking various affective reactions.  
   *Materials and Methods*  
   The study is based on data collected from a sample of travelers in the city of Santiago, in Chile. Participants in the study were asked about their usual mode of travel, and then were asked to name their ideal mode(s) of transportation from the perspective of various affective reactions. The reactions we investigate are associated with the values of freedom, enjoyment, happiness, poverty, luxury, and status. Analysis is based on tests of independence and visualization techniques.  
   *Results*  
   The results indicate that users of public transportation experience the most dissonance in terms of affective reactions, and active travelers the least. For those travelers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, whereas public transportation is most commonly associated with poverty. The automobile, in contrast, is the mode most commonly associated with luxury and status.

>>>>

---
title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
author:
  - name: Beatriz Mella Lira
    email: beatriz.lira.14@ucl.ac.uk
    affiliation: PUC
    footnote: Corresponding Author
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
address:
  - code: PUC
    address: BRT+ Centre of Excellence, Departamento Ingeniería de Transporte y Logística, Escuela de Ingeniería, Pontificia Universidad Católica de Chile
  - code: McMaster University
    address: School of Earth, Environment, and Society, McMaster University, 1280 Main St W, Hamilton, Ontario, L8S 1S4 Canada
abstract: |
   *Introduction*  
   Subjective wellbeing is a topic that has attracted considerable attention in the transportation literature in recent years. As a result, there is a burgeoning literature that investigates the impacts of travel on subjective wellbeing, and how wellbeing, in turn, can influence behavior. An important aspect of subjective wellbeing are the affective reactions of people to their experiences.   
   *Objective*  
   The objective of this paper is to analyze the affective reactions of travelers with respect to various modes of transportation. In particular, we are interested in the potential for dissonance between primary mode of travel and the mode(s) of travel identified as evoking various affective reactions.  
   *Materials and Methods*  
   The study is based on data collected from a sample of travelers in the city of Santiago, in Chile. Participants in the study were asked about their usual mode of travel, and then were asked to name their ideal mode(s) of transportation from the perspective of various affective reactions. The reactions we investigate are associated with the values of Freedom, Enjoyment, Happiness, Poverty, Luxury, and Status. Analysis is based on tests of independence and visualization techniques.  
   *Results*  
   The results indicate that users of public transportation experience the most dissonance in terms of affective reactions, and active travelers the least. For those travelers who experience dissonance, active travel is the mode most commonly associated with Freedom, Enjoyment, and Happiness, while public transportation is most commonly associated with Poverty. The automobile, in contrast, is the mode most commonly associated with Luxury and Status.

### 2021-01-14 Dissonance_Santiago_v3/Dissonance_Santiago_Title_Page_v3.tex
v3 Revisions after comments from anonymous reviewers, Journal of Transport and Health

@@

  \begin{abstract}
  \emph{Introduction}\\
  Subjective wellbeing is a topic that has attracted considerable
  attention in the transportation literature in recent years. As a result,
  there is a burgeoning literature that investigates the impacts of travel
  on subjective wellbeing, and how wellbeing, in turn, can influence
  behavior. An important aspect of subjective wellbeing are the affective
  reactions of people to their experiences.\\
  \emph{Objective}\\
  The objective of this paper is to analyze the affective reactions of
  travelers with respect to various modes of transportation. In
  particular, we are interested in the potential for dissonance between
  primary mode of travel and the mode(s) of travel identified as evoking
  various affective reactions.\\
  \emph{Materials and Methods}\\
  The study is based on data collected from a sample of travelers in the
  city of Santiago, in Chile. Participants in the study were asked about
  their usual mode of travel, and then were asked to name their ideal
  mode(s) of transportation from the perspective of various affective
  reactions. The reactions we investigate are associated with the values
  of freedom, enjoyment, happiness, poverty, luxury, and status. Analysis
  is based on tests of independence and visualization techniques.\\
  \emph{Results}\\
  The results indicate that users of public transportation experience the
  most dissonance in terms of affective reactions, and active travelers
  the least. For those travelers who experience dissonance, active travel
  is the mode most commonly associated with freedom, enjoyment, and
  happiness, whereas public transportation is most commonly associated
  with poverty. The automobile, in contrast, is the mode most commonly
  associated with luxury and status.
  \end{abstract}

>>>>

% Pandoc citation processing

@@

  \begin{abstract}
  \emph{Introduction}\\
  Subjective wellbeing is a topic that has attracted considerable
  attention in the transportation literature in recent years. As a result,
  there is a burgeoning literature that investigates the impacts of travel
  on subjective wellbeing, and how wellbeing, in turn, can influence
  behavior. An important aspect of subjective wellbeing are the affective
  reactions of people to their experiences.\\
  \emph{Objective}\\
  The objective of this paper is to analyze the affective reactions of
  travelers with respect to various modes of transportation. In
  particular, we are interested in the potential for dissonance between
  primary mode of travel and the mode(s) of travel identified as evoking
  various affective reactions.\\
  \emph{Materials and Methods}\\
  The study is based on data collected from a sample of travelers in the
  city of Santiago, in Chile. Participants in the study were asked about
  their usual mode of travel, and then were asked to name their ideal
  mode(s) of transportation from the perspective of various affective
  reactions. The reactions we investigate are associated with the values
  of Freedom, Enjoyment, Happiness, Poverty, Luxury, and Status. Analysis
  is based on tests of independence and visualization techniques.\\
  \emph{Results}\\
  The results indicate that users of public transportation experience the
  most dissonance in terms of affective reactions, and active travelers
  the least. For those travelers who experience dissonance, active travel
  is the mode most commonly associated with Freedom, Enjoyment, and
  Happiness, while public transportation is most commonly associated with
  Poverty. The automobile, in contrast, is the mode most commonly
  associated with Luxury and Status.
  \end{abstract}
